ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-07 paper/paper.tex
update

\subsection{Gradient boosted trees}
A gradient boosted trees $F_m(x)$ is updated as follows for a new tree $f_m$ built at iteration $m$ is

@@

We only applied stacking on task 2 but not task 1.
We tried two stacking method separately:
\begin{enumerate}
 \item 2-folds stacking split by two time frames

@@

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will outperform stacking using only one single algorithm.
Since we only used XGboost here, we compensated this by building several stacking features using randomized parameters to achieve diversification.

\textbf{Fig. 1} shows the $AUC$ of 5-folds Cross Validation using same parameters and seed and $AUC$ of prediction on 30\% of testing data .
 There is a strong correlation in $AUC$ between Cross Validation and 30\% of testing data.
 $AUC$ is improved once stacking is applied and we included more randomized stacking features until there is no improvement.

\begin{figure}[ht!]
\centering
\includegraphics[width=100mm]{Rplot.png}
\caption{$AUC$ of 5-folds CV result and 30\% testing data using different number of stacking features. The error bar represents one standard deviation of the CV score. \label{overflow}}
\end{figure}

@@

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{4.5cm}p{4cm}p{1cm}}
    \toprule
    Parameters & Description & Range of values & Final Choice \\
    \midrule
    $eta$ & Shrinkage & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of trees & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample ratio of data when constructing each tree & [0.7, 0.8, 0.9, 1] & 1 \\
    $gamma$ & Minimum loss reduction required to make a further partition & [0, 0.025, 0.05, 0.1, 0.3] & 0 \\
    $min\_child\_weight$ & minimum sum of instance weight (Hessian) required to make a further partition & [1, 3, 5, 7] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance and Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For task 1, we predicted the probability of visiting a particular branch for each customer using $logloss$ as the local evaluation metric.
 We selected top 5 branches with highest probability score. The $cosine@5$ on 30\% of the testing data is $\sim0.65$.

>>>>

\subsection{Gradient boosted trees}
A gradient boosted trees $F_m(x)$ is updated as follows for every new tree $f_m$ built at iteration $m$:

@@

We only applied stacking for task 2 but not task 1.
We tried two stacking method separately:
\begin{enumerate}
 \item 2-folds stacking split by two time frames

@@

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will outperform stacking using only one single algorithm.
Since we only used XGboost here, we compensated this by building multiple stacking features using randomized parameters to achieve diversification.

\textbf{Fig. 1} shows the task 2 $AUC$ of 5-folds Cross Validation using same parameters and the $AUC$ of prediction on 30\% of testing data.
 There is a strong correlation in $AUC$ between Cross Validation and 30\% of testing data.
 $AUC$ is improved once stacking is applied and we added more randomized stacking features until there is no improvement.

\begin{figure}[ht!]
\centering
\includegraphics[width=100mm]{Rplot.png}
\caption{Task 2 $AUC$ of 5-folds CV result (Same parameters) and Prediction on 30\% testing data using different number of stacking features.
 The error bar represents one standard deviation of the CV score. \label{overflow}}
\end{figure}

@@

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{4.5cm}p{4cm}p{1cm}}
    \toprule
    Parameters & Description & Grid Search Values & Final Choice \\
    \midrule
    $eta$ & Shrinkage & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of trees & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample ratio of data when constructing each tree & [0.7, 0.8, 0.9, 1] & 1 \\
    $gamma$ & Minimum loss reduction required to make a further partition & [0, 0.025, 0.05, 0.1, 0.3] & 0 \\
    $min\_child\_weight$ & Minimum sum of instance weight (Hessian) required to make a further partition & [1, 3, 5, 7] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance and Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For task 1, we predicted the probability of visiting a particular branch for each customer using $Logarithmic Loss$ as the local evaluation metric.
 We selected top 5 branches with highest probability score. The $cosine@5$ on 30\% of the testing data is $\sim0.65$.
